Legacy Data Confounds Genomics Studies

### 2019-07-09 LatexManuscript/legacy.tex
update to acknowledgments

\section{Author's Note}
\todo{While revising our manuscript for publication, in response to our pre-print, the New York Genome Center announced that they had resequenced the original 1kGP dataset in a yet to be published dataset.}

@@

\section{Acknowledgments}
We would like to thank Kelly Harris for sharing her mutation spectrum scripts.
\todo{We would like to thank Rajendra Mandage, Gabriel Santpere and Arcadi Navarro for sharing more details relating to the results from their publication.}
We would also like to thank the members of the Gravel lab for their help with coding and useful discussions.

>>>>

@@

\section{Acknowledgments}
We would like to thank K. Harris for sharing her mutation spectrum scripts, F. Mafessoni, G. Santpere and A. Navarro for feedback on earlier versions of the manuscript.
We would also like to thank the members of the Gravel lab for their help with coding and useful discussions.
